Accessible and Completed Datasets yet Majority are Bronze-Graded and not Updated Regularly with Missing Metadata

### 2025-05-15 paper/paper.qmd
Cleaned up data section and added areas of improvement for discussion section

From there the Data Quality Working Group were surveyed and asked to rank the importance of each dimension when it comes to assessing data quality where 1 represents the most important and 7 being the least important. The results from the survey would then help the team determine the weighting of each dimension towards the overall data quality score. Some of the dimensions were combined or removed. For example, granularity and interpretability were removed and interpretability was combined with usability. The team then used the ranking weighting method, Sum and Reciprocal, and obtain the following weights for each dimension alongside the type of questions asked for each dimension [@citeCatalogue; @citeCatalogueSteps]:

![Weight of the selected dimensions for data quality assessment and the metrics for each dimension](../other/images/weighting_of_dimensions.png)

@@

# Discussion {#sec-discussion}
In @sec-results, we

## Point 1

## Point 2

## Areas of improvement

>>>>

From there the Data Quality Working Group were surveyed and asked to rank the importance of each dimension when it comes to assessing data quality where 1 represents the most important and 7 being the least important. The results from the survey would then help the team determine the weight of each dimension towards the overall data quality score. Some of the dimensions were combined or removed. For example, granularity and interpretability were removed and interpretability was combined with usability. The team then used the ranking weighing method, Sum and Reciprocal, and obtain the following weights for each dimension alongside the type of questions asked for each dimension [@citeCatalogue; @citeCatalogueSteps]:

![Weight of the selected dimensions for data quality assessment and the metrics for each dimension](../other/images/weight.png)

@@

# Discussion {#sec-discussion}
In @sec-results, we looked at the data quality of 39,580 datasets on the Open Data Toronto

## Majority of Datasets are graded "Bronze"

## Bronze-graded datasets are less likely to update and have missing metadata

## Areas of improvement 
As mentioned in @sec-data, datasets have a higher usability score if their column names contains more English words. However, this criteria does not consider datasets that could be still useful but are not in English. Another limitation of our analysis is that the weight of the different dimensions in the data that goes towards the grade of a dataset is subjective in nature since the weighing is based on survey data that had people rank the perceived importance of each dimension.
